\documentclass[a4paper,10pt]{article}
\usepackage{geometry}
\geometry{left=0.5in, right=0.5in, top=0.5in, bottom=0.5in}
\usepackage{fontawesome}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{xcolor}
\usepackage{parskip}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\columnsep}{1.5em}
\pagestyle{empty}

\hypersetup{
	colorlinks=true,
	urlcolor=blue,
}

\titlespacing*{\section}{0pt}{1ex plus 1ex minus .2ex}{0.5ex plus .2ex}

\titleformat{\section}{\large\bfseries}{}{0pt}{}[\titlerule]

\begin{document}
	\small
	\begin{center}
		{\LARGE \textbf{Shivakumar Jagadam}} \\
		Rajiv Gandhi University Of Knowledge Technologies, Basar \\
		\faPhone\ +919701635557 \quad \faEnvelope\ \href{mailto:shivakumarjagadam@gmail.com}{shivakumarjagadam@gmail.com} \quad Nizamabad, Telangana, India \quad \href{https://www.linkedin.com/in/shivakumar-jagadam-12559425a/}{LinkedIn} \quad \href{https://github.com/Shivakumarjagadam}{Github}
	\end{center}
	
	\vspace{0.2cm}
	
	\section*{EDUCATION}
	\vspace{0.2cm}
	\noindent\textbf{B.Tech (CSE) - 8.5 CGPA} \hfill Jan 2022 - Present \\
	Rajiv Gandhi University of Knowledge and Technologies
	
	\vspace{0.2cm}
	
	\noindent\textbf{Pre-University Course - 9.3 CGPA} \hfill 2020 - 2022 \\
	Rajiv Gandhi University of Knowledge and Technologies
	
	\vspace{0.2cm}
	
	\noindent\textbf{Secondary School - 10 CGPA} \hfill 2020 \\
	Z.P.H.S Mirdhapalle.
	
	\vspace{0.2cm}
	
	\section*{PROJECTS}
	\begin{multicols}{2}
		
		
		\noindent\textbf{Email Software} \hfill \href{https://github.com/Shivakumarjagadam/WEB-TECHNOLOGY/tree/main/webTechnologies/projects_tomcat/GmailMini_project}{Github} \\
		
		
		\textbf{Tech Stack:} HTML | CSS | JSP | MySQL
		
		\begin{itemize}[leftmargin=*]
			\item \textbf{User Authentication:} Supports user registration and login.
			\item \textbf{Email Management:} Enables sending, receiving, and organizing emails. Users can manage their inbox, sent items, and trash.
			\item \textbf{Account Management:} Allows users to permanently delete their accounts.
		\end{itemize}
		\columnbreak
		
		\vspace{0.2cm}
		
		
		\noindent\textbf{Cricket Game} \hfill \href{https://shivakumarjagadam.github.io/New-Cricket-game/}{Github} \\
		
		\textbf{Tech Stack:} HTML | CSS | JavaScript
		
		Developed an interactive user vs computer cricket game where the score is updated dynamically based on the user's and computer’s actions.
		
	\end{multicols}
	
	\vspace{0.2cm}
	
	\section*{CERTIFICATIONS}
	\vspace{0.2cm}
	
	\begin{itemize}[noitemsep]
		\item Social Summer Of Code participant certification
		\hfill \href{https://certificate.givemycertificate.com/c/db9a71cb-ef77-42e9-84cb-80917fa263ad}{certificate link}
		\item JavaScript certification test 
	\end{itemize}
	
	\vspace{0.2cm}
	
	\section*{COURSEWORK}
	\begin{multicols}{2}
		\begin{itemize}[noitemsep]
			\item Data Structure and Algorithms
			\item Database Management Systems
			\item Object-Oriented Programming
			\item Operating Systems
			
		\end{itemize}
	\end{multicols}
	
	\vspace{0.2cm}
	
	\section*{EXPERIENCE}
	\vspace{0.2cm}
	
	\noindent\textbf{VSOC'24 Contributor} \hfill June 2024 - July 2024 \\
	\textit{Vinyasa Summer of Code} \hfill Remote \\
	Contributed to various open-source projects. \\
	Tech Stack: HTML,CSS,Javascript,React.
	
	\vspace{0.3cm}
	
	
	\noindent\textbf{SSOC'24 Contributor} \hfill June 2024 - Aug 2024 \\
	\textit{Social Summer of Code} \hfill Remote \\
	Contributed to various open-source projects. \\
	Tech Stack: HTML,CSS,Javascript,React,Bootstrap.
	
	
	\vspace{0.2cm}
	
	\section*{ACHIEVEMENTS}
	\vspace{0.2cm}
	
	\begin{itemize}[noitemsep]
		\item NMMS Scholar 2019 - 2020
		\item Solved 100+ standard DSA problems on Leetcode and GFG
		\item Achieved 4 star in Hackerrank JAVA Programming
	\end{itemize}
	
	\vspace{0.2cm}
	
	\section*{TECHNICAL SKILLS}
	\begin{multicols}{2}
		\textbf{Programming Languages:} C, C++, Java \\
		\textbf{Scripting Languages:} Python, JavaScript \\
		\textbf{Web Development:} Html,Css,Javascript,Bootstrap,React \\
		\columnbreak
		\textbf{Database:} MySQL \\
		\textbf{Version Control:} Git, GitHub \\
		\textbf{Tools:} Visual Studio Code \\
		\textbf{Operating Systems:} Linux, Windows
	\end{multicols}
	
	
	\section*{INTEREST}
	\vspace{0.2cm}
	
	\begin{itemize}[]
		\item Listening to music
		\item Fitness
		\item Reading
	\end{itemize}
	
	\vspace{0.2cm}
	
\end{document}